Project 2

### 2018-10-01 Project2/report/Project2.tex
Finished intro

\subsection{Quantum dots, one electron}
Studying a case of one electron by adding a quantum harmonic oscillator potential to our tridiagonal matrix. The numerical precision from applying Jacobi's method to Toepliz matrix, is reduced under the now more complex tridiagonal matrix. To achieve four leading digits it becomes necessary to increase matrix size to $n = 380$. This is a result of probability function calculated for the ground state energy, which now requires a stable balance between interval size $\rho$ and matrix size $n$. As seen in [fig:\ref{fig:fig2}] the interval size $\rho$ governs our approximation of infinity in the potential, however letting this interval increase requi

>>>>

\subsection{Quantum dots, one electron}
Studying a case of one electron by adding a quantum harmonic oscillator potential to our tridiagonal matrix. The numerical precision from applying Jacobi's method to Toepliz matrix, is reduced under the now more complex tridiagonal matrix. To achieve four leading digits it becomes necessary to increase matrix size to $n = 380$. This is a result of probability function calculated for the ground state energy, which now requires a stable balance between interval size $\rho$ and matrix size $n$. As seen in [fig:\ref{fig:fig2}] the interval size $\rho$ governs our approximation of infinity in the potential, however letting this interval increase requires that matrix size increases along with the
